Inference methods comparison for the simplified Naomi model

### 2023-02-07 src/naomi-simple_compare/comparison.Rmd
Add ECDF plot to histogram

```{r}
beta_rho <- histogram_plot("beta_rho", i = 1, return_df = TRUE)
beta_rho$plot
saveRDS(beta_rho$df, "beta_rho.rds")

histogram_plot("beta_anc_rho")
```

>>>>

```{r}
beta_rho <- histogram_and_ecdf("beta_rho", i = 1, return_df = TRUE)
beta_rho$plot
saveRDS(beta_rho$df, "beta_rho.rds")

histogram_and_ecdf("beta_anc_rho")
```

```{r}
par <- "beta_rho"
i <- 1
par_name <- paste0(par, "[", i, "]")

df_compare <- rbind(
  data.frame(method = "TMB", samples = as.numeric(tmb$fit$sample[[par]][i, ])),
  data.frame(method = "aghq", samples = as.numeric(aghq$quad$sample[[par]][i, ])),
  data.frame(method = "adam", samples = as.numeric(adam$sample[[par]][i, ])),
  data.frame(method = "tmbstan", samples = as.numeric(unlist(rstan::extract(tmbstan$mcmc, pars = par)[[par]][, i])))
)

grid <- seq(from = min(df_compare$samples), to = max(df_compare$samples), by = 0.1)

tmb_ecdf <- stats::ecdf(filter(df_compare, method == "TMB") %>% pull(samples))
tmb_ecdf_df <- data.frame(x = grid, ecdf = tmb_ecdf(grid), method = "TMB")

aghq_ecdf <- stats::ecdf(filter(df_compare, method == "aghq") %>% pull(samples))
aghq_ecdf_df <- data.frame(x = grid, ecdf = aghq_ecdf(grid), method = "aghq")

adam_ecdf <- stats::ecdf(filter(df_compare, method == "adam") %>% pull(samples))
adam_ecdf_df <- data.frame(x = grid, ecdf = adam_ecdf(grid), method = "adam")

tmbstan_ecdf <- stats::ecdf(filter(df_compare, method == "tmbstan") %>% pull(samples))
tmbstan_ecdf_df <- data.frame(x = grid, ecdf = tmbstan_ecdf(grid), method = "tmbstan")

bind_rows(tmb_ecdf_df, aghq_ecdf_df, adam_ecdf_df, tmbstan_ecdf_df) %>%
  mutate(method = forcats::fct_relevel(method, levels = c("TMB", "aghq", "adam", "tmbstan"))) %>%
  ggplot(aes(x = x, y = ecdf, col = method)) +
    geom_line() +
    scale_color_manual(values = multi.utils::cbpalette()) +
    labs(x = "", y = "ECDF") +
    theme_minimal()

```
